### 2016-03-17 paper.tex
Stub the other sections

>>>>

\section{Cultural Empathy and Monsters}

\textit{Kay will write something here that justifies the idea of using this kind of game to teach cultural empathy, using Monsters as a hook}

\section{Design Experiment}

\textit{Paco will describe the team that undertook the design challenge, including the articulation of our three goals and the design elements being used to realize them}

\section{Pilot Study}

\textit{In which we describe what playtesting has revealed to us}

\section{Conclusions and Future Work}

\textit{In which we make and justify some conclusions, and point toward
 other areas that this work could be extended}
